---
title: "A simple map application"
author: "Alejandro Borges Sanchez"
date: "6/22/2021"
output: ioslides_presentation
---

## Breweries dataset

OKay, some somewhat advanced for what weve seen so far, but there exists a dataset listing some breweries in germany. It is not a normal dataframe, but a spatial points dataframe, which are data structures designed for geo/spatial operations. Look at it!

```{r}
library(leaflet)
data("breweries91")
br<-breweries91
```

## Breweries dataset

```{r }

str(br)
```

## Breweries dataset

-   So you can see this dataset is an object (denoted by having attributes with the \@ sign before them), and one of them is "data" which is the data itself *brewery, address...*, and then all the rest are attributes for geospatial operations: *coordinates, bounding boxes, projection string*...

## So whats up!?

### Lets fly to germany and see where we gonna pound down some cold ones!

-   This objects are called "st" objects and leaflet knows nothing about them.
-   Leaflet prefers dataframes with lat, long variables or a more modern kind of spatial dataframe called "sf", from the sf package (spatial features)
-   Now lets see where we gonna go drink some!

## Find your brewer!

```{r echo=FALSE}
library(sf)
sf::st_as_sf(breweries91)%>%
    leaflet()%>%
    addTiles()%>%
    addMarkers(popup = ~paste0("Name: ",brewery,"<br>",
                               "Address: ",address,"<br>",
                               "Village: ",village,"<br>",
                               "Founded: ",founded,"<br>"))
```

### The code is in the next page

## Code

```{r eval=FALSE}
sf::st_as_sf(breweries91)%>%
    leaflet()%>%
    addTiles()%>%
    addMarkers(popup = ~paste0("Name: ",brewery,"<br>",
                               "Address: ",address,"<br>",
                               "Village: ",village,"<br>",
                               "Founded: ",founded,"<br>"))
```

### Not to toot my own horn, but you can see how to add popups to the markers so they show data
